### 2018-09-06 ICRA19/covControl.tex
Checked the math for angle of repose, small updates
Some more todos for Shiva & Haoran

\subsection{Hardware experiment: angle of repose}
In this section we vary the force and approach angle to shape a swarm with a characteristic angle of repose.

@@

\textcolor{red}{Explain hardware experiment}

>>>>

\subsection{Hardware experiment: particle angle of repose}
In this section we vary the force and approach angle to shape a swarm with a characteristic angle of repose.

@@

\textcolor{red}{TODO: Haoran will Explain hardware experiment}

\subsection{Hardware experiment: kilobot angle of repose}
In this section we vary the force and approach angle to shape a swarm with a characteristic angle of repose.

\textcolor{red}{TODO: Shiva will insert the kilobot images and a couple of sentences, and a couple of sentences about kilobots}

### 2018-09-06 ICRA19/intro.tex
added more todos and blank photos
Some more todos for Shiva & Haoran

@@

 Positioning is a foundational capability for a robotic system, e.g. placement of brachytherapy seeds. 
 In previous work, we provided position control algorithms that only require non-slip wall contacts to position two robots \cite{shahrokhi2017}
We assumed that particles in contact with the boundaries have zero velocity if the uniform control input pushes the particle into the wall. This work analyses interactions between the boundary and the particle swarm to control shape of the swarm. In \cite{shahrokhi2018TRO} we showed how to control swarm statistics including mean position and variance. This work extends that work to covariance control.

>>>>

   \textcolor{red}{TODO: this text is from a previous paper}

@@

 Positioning is a foundational capability for a robotic system, e.g. placement of brachytherapy seeds. 
 In previous work, we provided position control algorithms that only require non-slip wall contacts to position two robots \cite{shahrokhi2017}. 
We assumed that particles in contact with the boundaries have zero velocity if the uniform control input pushes the particle into the wall. This work analyses interactions between the boundary and the particle swarm to control shape of the swarm. In \cite{shahrokhi2018TRO} we showed how to control swarm statistics including mean position and variance. This work extends that work to covariance control.

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{leadfigure.pdf}%\put(1,55){a)}
\end{overpic}
\caption{\label{fig:leadfigure} 
      \textcolor{blue}{TODO: we need a lead figure in column 1:   Combine kilobots from Fig 3 and 4 with photos of angle of repose by Haoran of iron with 4 rod angles. }
}
\end{figure}
